### 2017-05-26 2017/NACO/paper.tex
Fix two references in the Globalizer paper

\section{Globalizer System Architecture}
\label{sec:arch}
Globalizer expands the family of the global optimization software systems developed
by the authors during the past several years. One of the first developments was the
SYMOP multiextremal optimization system \cite{gergel1993}, which has been applied for solving
many optimization problems. The ExaMin system \cite{barkalovGergel2015}, [3], [4], [16] was developed
and used to investigate various parallel algorithms for solving the global
optimization problems on the high-performance computational systems.

>>>>

\section{Globalizer System Architecture}
\label{sec:arch}
Globalizer expands the family of the global optimization software systems developed
by the authors during the past several years. One of the first developments was the
SYMOP multiextremal optimization system \cite{gergel1993}, which has been applied for solving
many optimization problems. The ExaMin system \cite{barkalovGergel2015}, \cite{barkalovGergelLebedev2015},
\cite{barkalovGergelLebedevSysoev2015}, \cite{gergelLebedev2015} was developed
and used to investigate various parallel algorithms for solving the global
optimization problems on the high-performance computational systems.
